Analyzing DECREASE trials for extent of data fabrication

### 2016-04-15 submission/manuscript.Rmd
Interim commit

@@

@@

clip(x1 = 0, x2 = length(res_iv_uncertain), y1 = 0.025, y2 = .975)
abline(v = which(abs(res_iv_uncertain - .975) == min(abs(res_iv_uncertain - .975))), lty = 1)
abline(v = which(abs(res_iv_certain - .975) == min(abs(res_iv_certain - .975))), lty = 2)

```

>>>>

# load('data/result_almost_i_uncertain')
# load('data/result_almost_i_certain')
# 
# load('data/result_almost_iv_uncertain')
# load('data/result_almost_iv_certain')

@@

legend(x = 0, y = .5, bty = 'n', lty = c(1, 2), legend = c("Distribution estimate", "Point estimate"))

@@

legend(x = 0, y = .55, bty = 'n', lty = c(1, 2), legend = c("Distribution estimate", "Point estimate"))

clip(x1 = 0, x2 = length(res_iv_uncertain), y1 = 0.025, y2 = .975)
abline(v = which(abs(res_iv_uncertain - .975) == min(abs(res_iv_uncertain - .975))), lty = 1)
abline(v = which(abs(res_iv_certain - .975) == min(abs(res_iv_certain - .975))), lty = 2)
```

| -           | Estimate              | Lowerbound  | Upperbound | N    |
|-------------|-----------------------|-------------|------------|------|
| DECREASE-I  | Distribution estimate | 0           | 79;85;90   | 113  |
| -           | Point estimate        | 0           | 108;110    | 113  |
| DECREASE-IV | Distribution estimate | 0           | 1054       | 1067 |
| -           | Point estimate        | 0           | 718        | 1067 |
